% !TeX root = thesis.tex
\def\slet#1#2{\expandafter\let\csname#1\expandafter\endcsname\csname#2\endcsname}
\addto\begitems{\slet{normalitem}{item:o}}


\app Thesis assignment

%\picw=\hsize \cinspic resources/images/assignment.png

\nextoddpage

\app List of Abbreviations \par \makeglos

\nextoddpage

\label[ap.questionnaires]
\app Usability test questionnaires

\label[screener]
\sec Screener

	\begitems
		*Are you a smarphone user?
		*Are you a driver?
		*How many times per week are you driving?
	\enditems

\label[pretest]
\sec Pre-test questionnaire
	
	
	\begitems
		*Age,
		*Sex [male, female],
		*How many kms per year are you driving a car?
		*Which operating system is your smartphone running?
		*Have you ever used your smartphone while driving? [yes, no]
		*How often are you using your smartphone while driving? [never, occasionaly, often]
	\enditems

\label[posttest]
\sec Post-test questionnaire

In [1-5] questions, 1 means the best rating, 5 means the worst.

	\begitems
		*What is your impression of using the device while driving? [1-5]
		*Were the goals clear for your? [yes, no]
		*How acceptable was the way of solution for given tasks? [1-5]
		*Was the amount of displayed information appropriate? [1-5]
		*Would you use the application in everyday driving time? [1-5]
	\enditems

\nextoddpage

\label[tests_results]
\app Usability test results analysis

\sec{MATLAB scripts}

\secc Statictics of A/B testing

\begtt

clear all;

load('p4_ab_m_cd.mat');
tablet = [116;97;98;108;101;116];
phone = [112;104;111;110;101];
objectname = phone;
comparation = ismember(ClosestWorldIntersection_objName(
						(1:length(objectname)),:),objectname);

watchingPhone = comparation(2,:);
totalPhone = sum(watchingPhone);

glanceRatio = totalPhone / length(ClosestWorldIntersection_objName);

glanceRatio

totalPhone

length(ClosestWorldIntersection_objName)

inputvector = watchingPhone;

glances = [];
currentGlance = 0;
for n = 2:numel(inputVector)
    if(inputVector(n))
        if(inputVector(n-1))
            currentGlance = currentGlance +1;
        end
    else
        if(inputVector(n-1))
            glances = [glances, currentGlance];
            currentGlance = 0;
        end
    end
end


if(currentGlance>0)
    glances = [glances, currentGlance];
    currentGlance = 0;
end

numOfGlances = length(glances)
maxGlance = max(glances)*1000/60
averageGlance = sum(glances)/length(glances)*1000/60
\endtt

\secc Visualisation of Lane change test

\begtt

steerDiff = find(diff(steer)<-2); 
\%steering more than treshold (id, where was the steering bigger)

yL = get(gca,'YLim'); \% length of Y

\%objectX = -5400.7-1.1; objectY = 2296.6-1.1;
objectX = -5239.3-1.1;  objectY = 2292-1.1;

middle = plot(x,-z,'Color',[0 0 1]);
hold on;
lSide = plot(x,-z-1, 'Color', [0.8 0.8 1]);
rSide = plot(x,-z+1, 'Color', [0.8 0.8 1]);
axis equal;
axis ([objectX-60 objectX+40 objectY-6 objectY+15]);
yL = get(gca,'YLim'); \% length of Y
set(gca,'xtick',[],'ytick',[])
steeringStarted = line([x(steerDiff(1)) x(steerDiff(1))],yL,
						'Color',[0 1 0]); 
\% drive line, where the plotting started

objectShown = line([objectX-35 objectX-35],yL,'Color',[1 0 0]); 
\% line where object appeard


legend('Middle of the car', 'Border of the car', 
'Border of the car', 'Start of steering','Object was shown'  );



rectangle('Position',[objectX objectY 2.2 2.2]); \%5400.7, 1.1, 2296.6
\%rectangle('Position',[-5238.2 2290.9 2.2 2.2]); \%5239.3, 1.1, 2292
reactionTime = x(steerDiff(1))- (-5399.6-35);
hold off;

\endtt

\sec Results of Lane Change Test

\midinsert \clabel[lct_res1]{Lane Change Test - Participant \#1}
\picw=\hsize \cinspic resources/images/tests/lct1.pdf
\caption/f Lane Change Test - Participant \#1
\endinsert

\midinsert \clabel[lct_res2]{Lane Change Test - Participant \#2}
\picw=\hsize \cinspic resources/images/tests/lct2.pdf
\caption/f Lane Change Test - Participant \#2
\endinsert

\midinsert \clabel[lct_res3]{Lane Change Test - Participant \#3}
\picw=\hsize \cinspic resources/images/tests/lct3.pdf
\caption/f Lane Change Test - Participant \#3
\endinsert

\midinsert \clabel[lct_res4]{Lane Change Test - Participant \#4}
\picw=\hsize \cinspic resources/images/tests/lct4.pdf
\caption/f Lane Change Test - Participant \#4
\endinsert

\midinsert \clabel[lct_res5]{Lane Change Test - Participant \#5}
\picw=\hsize \cinspic resources/images/tests/lct5.pdf
\caption/f Lane Change Test - Participant \#5
\endinsert


\nextoddpage

\app Content of the CD

\begtt

E:.
|---cardashboard
|---usability tests


\endtt



