\input template/ctustyle
\input opmac-bib
\worktype [M/EN]
\faculty {F3}
\department {Department of Computer Science and Engineering}
\title {Car infotainment application on~a~smartphone}
\author {Lukáš Hrubý}
\supervisor{Ing. Jan Šedivý, CSc.}
\date {January 2016}
\abstractEN {Abstract in english. \rfc{add abstracts}}
\abstractCZ {Abstakt v cestine.}
\declaration {I hereby declare that I worked out the presented thesis independently and I quoted all the sources used in this thesis in accord with Methodical instructions about ethical principles for writing academic thesis. 

Prague, 11th January 2016 \signature

\hfil\break\hfil\break\hfil\break\hfil\break\hfil\break

Prohlašuji, že jsem předloženou práci vypracoval samostatně, a že jsem uvedl veškeré použité informační zdroje v souladu s Metodickým pokynem o dodržování etických principů při přípravě vysokoškolských závěrečných prací.

V Praze dne 11. ledna 2016 \signature
}
\thanks{
I would like to thank the supervisor of this thesis, Ing.~Jan~\v Sediv\' y,~CSc., for the continous support, for his motivation, enthusiasm, and advices he has given me over the past two years. 

Beside my supervisor, my sincere thanks also goes to the members of Driving Simulation Research Group of Faculty of Transportation Sciences of Czech Technical University in Prague for all the help and patience with testing and everything related. 

I would also like to thank my college, Bc. Michael Bl\'aha for cooperating and advicing throughout the whole thesis development process. 

Last but not the least, I thank my family and friends for supporting me the whole time in my studies and life.

\hfil\break

This work was partially supported by CZECH TECHNICAL UNIVERSITY MEDIA LABORATORY foundation.}

\draft

\input glosdata
\makefront

\input 01introduction
\nextoddpage

\input 02analysis
\nextoddpage

\input 03design
\nextoddpage

\input 04execution
\nextoddpage

\input 05evaluation
\nextoddpage

\input 06conclusion
\nextoddpage

\bibchap
\usebib/c (simple) resources/references.bib
\input appendix
\bye